Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-27 paper.tex
Edit participants

\subsubsection{Registrar}
Registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.

\subsubsection{Data Provider}
Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network. An MAM channel\cite{MAM} is used to store encrypted data stream.

@@

\subsection{Component}
\subsubsection{IOTA}
IOTA\cite{IOTAwhitepaper} is a cryptocurrency which the ledger does not consist of transactions grouped into blocks and stored in sequential chains, but a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}. To issue a transaction in the network, one needs to perform a small amount of Proof-of-Work (PoW) that verifies two previous transactions. Since every actor in Tangle has the same role, there is no need to offer transaction fees. Therefore, it is possible to make \textbf{micropayments} which the importance will increase in the rapidly developing IoT industry, and \textbf{zero-transactions} that one could store information securely within Tangle transactions. Moreover, this structure also enables high scalability of transactions that could resolve the drawbacks of blockchain and the concern of rapid growth of IoT devices.

\subsubsection{smart contract}

\subsubsection{IPFS}

\subsubsection{MAM}

\subsubsection{TangleID}

\subsubsection{blind signature}

>>>>

\subsubsection{Registrar}
Registrar is responsible for creating a Registration Contract, which preserves a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.

\subsubsection{Data Provider}
Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data with their sensors and send it to the broker who will assist in uploading it to the network. A MAM channel\cite{MAM} is used to store  encrypted data stream.

@@
